`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
fixed a couple of typos in captions
updated appendix

   	\caption{An example of continuous field decomposed by a finite number of basis functions scaled by the state vector. } 

@@

@@

@@

% The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  

@@

The matrix $\Gamma$ is defined as the inner product of the field basis function vector as
	\boldsymbol\Gamma = \left[
		\Gamma_{1,1} & \dots & \Gamma_{1,L} \\
		\Gamma_{L,1} & \dots & \Gamma_{L,L} 
	\right],

@@

\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.

@@

 \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r).

@@

 \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r).

@@

\phi_i\otimes\phi_j&=&\int_{\mathbb{R}^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathbb{R}^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i).

@@

Evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives

@@

 \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).

>>>>

   	\caption{An example of a continuous one-dimensional continuous field decomposed by a finite number of basis functions scaled by the state vector.} 

@@

\begin{equation}\label{eq:n_dimensional_Gaussian1}

@@

\begin{equation}\label{eq:n_dimensional_Gaussian2}

@@

The analytic definition of the observation matrix, $C$, and the matrix $\boldsymbol\Psi(\mathbf{r})$ are formulated using this derivation.  

@@

The inner product of the two \emph{n}-dimensional Gaussians (from equations~\ref{eq:n_dimensional_Gaussian1} and~\ref{eq:n_dimensional_Gaussian2}) is defined as

@@

\varphi_i\otimes\varphi_j=\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf{r}.

@@

 \varphi_i(\boldsymbol \mu_i+\mathbf r)= \varphi_i(\boldsymbol \mu_i-\mathbf r).

@@

 \varphi_i(\mathbf r)= \varphi_i(2\boldsymbol \mu_i-\mathbf r).

@@

\varphi_i\otimes\varphi_j&=&\int_{\mathbb{R}^n}\varphi_i(\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathbb{R}^n}\varphi_i(2\boldsymbol \mu_i-\mathbf r)\varphi_j(\mathbf r)d\mathbf r\\
&=&(\varphi_i*\varphi_j)(2\boldsymbol \mu_i).

@@

Evaluating equation~\ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives

@@

 \varphi_i\otimes\varphi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
